Research Notes

### 2020-06-22 notes/notes.tex
June 22 Notes; gitignore plots

\section{Friday, June 19}
    \begin{enumerate}
        \item Looking over code
        \begin{enumerate}
            \item Might be too slow, move to C/C++ eventually?
            \item Why is the energy increasing with metropolis algorithm?
            \item Shift to using action instead of Hamiltonian.
            \item Transition from Broken Phase, look at $\mu_0^2$ term.
            \item Profile code for possible optimizations.
        \end{enumerate}
    \end{enumerate}

>>>>

\section{Friday, June 19}
    \begin{enumerate}
        \item Looking over code
        \begin{enumerate}
            \item Might be too slow, move to C/C++ eventually?
            \item Why is the energy increasing with metropolis algorithm?
            \item Shift to using action instead of Hamiltonian.
            \item Transition from Broken Phase, look at $\mu_0^2$ term.
            \item Profile code for possible optimizations. % http://users.physik.fu-berlin.de/~kleinert/kleiner_reb8/psfiles/phi4.pdf
        \end{enumerate}
    \end{enumerate}

 \section{Monday, June 22}
    \begin{enumerate}
        \item Coding
        \begin{enumerate}
            \item Add plots to \texttt{.gitignore}.
            \item Try parallelizing code, using either multigrid or checkerboard algorithm
        \end{enumerate}

        \item Reading
        \begin{enumerate}
            \item Start to focus more on understanding the theory behind research.
            \item Read dissertation \cite{Schaich2006} Chap. 6.5 and 6.6, take notes on questions.
            \item Newman \cite{Newman1999} (Main textbook for Monte Carlo in Statistical Physics)
        \end{enumerate}

        \item Just some things to remember
        \begin{enumerate}
            \item Correlation functions correlate values in statistical systems and relate to propagators in QFT.
            \item The problem of renormalization: $a\rightarrow0$ leads to unbounded correlation function. As real physical lengths are measured in terms of the lattice constant, these sometimes tend to infinity.
        \end{enumerate}
    \end{enumerate}
